---
title: MOOC-Generator that access Google APIs
output: 
  html_document:
    theme: cosmo
    toc: yes
---

<!--
Heavily inspired by:
https://github.com/tidyverse/tidyverse.org/blob/master/content/google_privacy_policy.md
-->

## Goal of OAuth with MOOC-generator

The goal of the MOOC-generator is to allow users to use `R` packages such as `didactr` to create videos.  The authentication of the MOOC-generator allows users to look for Google Slide decks on their Google Drive account.  Once a slide deck is selected, the contents of the Google Slide can then be downloaded and converted to a set of PNGs, along with any notes on the slides.  The PNGs with the notes can then be combined into a video.  We use the notes with services such as Amazon Polly, Google Language, and Microsoft Bing to synthesize the text into audio (not covered by the MOOC-generator authentication).  The audio is then overlaid on the slides to create the video.  Once the video is located, the `didactr` package allows users to upload these vidoes to their channel using the YouTube API.  Other packages authenticate users in these domains individually, the MOOC-generator allows for authentication in all of these APIs to have a coherent workflow and only one authentication procedure.

We aim to create educational and instructional videos.  You can see example of an output video we have created for Johns Hopkins at https://www.youtube.com/watch?v=W7Wn2CWThVk.  These goals are a part of the Johns Hopkins Data Science Lab (https://jhudatascience.org/) and will be used for courses such as Cloud-Based Data Science (https://leanpub.com/universities/set/jhu/cloud-based-data-science).  No information from the user is stored other than the number of users that are using the application and the API requsts from each user and what is recorded on Google Projects dashboards for all API-based projects.

## Disclaimer and Privacy Policy

Your use of Google APIs with these packages is subject to each API's respective
terms of service. See <https://developers.google.com/terms/>.  The Privacy statement can be seen [here](../google_privacy_policy.html).


## Use cases

### Authentication 
We will show how to use the `didactr` R package to authorize the MOOC generator.  Here we will show the authetication, using `didactr_auth`:

```{r no_show_token, eval = FALSE}
library(didactr)
token = didactr_auth()
token
```

```{r read_token, eval = TRUE, message=FALSE, echo = FALSE}
library(didactr)
token = readRDS("google_token.rds")
check_didactr_auth(token = token)
token
```

We see the output is an authorized token. We could have also saved this token and passed it into the `token` argument of `didactr_auth`.

### Scopes 

 We can see the scopes that are authorized:

```{r token}
token$credentials$scope
```

### Checking Authentication

If you would like to check, in code, if you are authorized, you can use the `check_didactr_auth` function, which will return a logical indicating if the app has been authorized:

```{r checking}
check_didactr_auth()
```

### Finding a Slide Presentation (Google Drive Auth)

As you are authorized for Google Drive with MOOC-generator, let's say you want to find a Google Slide deck:

```{r get_drive, eval = FALSE}
res = googledrive::drive_find("Leanpub", type = "presentation")
res
```

```{r get_drive_show, echo = FALSE}
res = structure(list(name = "Leanpub_MOOCs_JHU", id = "1Opt6lv7rRi7Kzb9bI0u3SWX1pSz1k7botaphTuFYgNs", 
    drive_resource = list(list(kind = "drive#file", id = "1Opt6lv7rRi7Kzb9bI0u3SWX1pSz1k7botaphTuFYgNs", 
        name = "Leanpub_MOOCs_JHU", mimeType = "application/vnd.google-apps.presentation", 
        starred = FALSE, trashed = FALSE, explicitlyTrashed = FALSE, 
        parents = list("0AKBXs4DhNbzBUk9PVA"), spaces = list(
            "drive"), version = "83", webViewLink = "https://docs.google.com/presentation/d/1Opt6lv7rRi7Kzb9bI0u3SWX1pSz1k7botaphTuFYgNs/edit?usp=drivesdk", 
        iconLink = "https://drive-thirdparty.googleusercontent.com/16/type/application/vnd.google-apps.presentation", 
        hasThumbnail = TRUE, thumbnailLink = "https://docs.google.com/feeds/vt?gd=true&id=1Opt6lv7rRi7Kzb9bI0u3SWX1pSz1k7botaphTuFYgNs&v=28&s=AMedNnoAAAAAXS4Et7-RKTOfNQvXLcfskEFO2bQ1qKCN&sz=s220", 
        thumbnailVersion = "28", viewedByMe = TRUE, viewedByMeTime = "2019-07-16T15:08:32.582Z", 
        createdTime = "2019-04-16T19:09:07.060Z", modifiedTime = "2019-04-18T17:03:14.356Z", 
        modifiedByMeTime = "2019-04-18T17:03:14.356Z", modifiedByMe = TRUE, 
        owners = list(list(kind = "drive#user", displayName = "John Muschelli", 
            photoLink = "https://lh3.googleusercontent.com/-XP36b9P_2u4/AAAAAAAAAAI/AAAAAAAAAFU/duLcXDs5KAE/s64/photo.jpg", 
            me = TRUE, permissionId = "15237212639967747286", 
            emailAddress = "muschellij2@gmail.com")), lastModifyingUser = list(
            kind = "drive#user", displayName = "John Muschelli", 
            photoLink = "https://lh3.googleusercontent.com/-XP36b9P_2u4/AAAAAAAAAAI/AAAAAAAAAFU/duLcXDs5KAE/s64/photo.jpg", 
            me = TRUE, permissionId = "15237212639967747286", 
            emailAddress = "muschellij2@gmail.com"), shared = TRUE, 
        ownedByMe = TRUE, capabilities = list(canAddChildren = FALSE, 
            canChangeCopyRequiresWriterPermission = TRUE, canChangeViewersCanCopyContent = TRUE, 
            canComment = TRUE, canCopy = TRUE, canDelete = TRUE, 
            canDownload = TRUE, canEdit = TRUE, canListChildren = FALSE, 
            canMoveItemIntoTeamDrive = TRUE, canMoveItemOutOfDrive = TRUE, 
            canReadRevisions = TRUE, canRemoveChildren = FALSE, 
            canRename = TRUE, canShare = TRUE, canTrash = TRUE, 
            canUntrash = TRUE), viewersCanCopyContent = TRUE, 
        copyRequiresWriterPermission = FALSE, writersCanShare = TRUE, 
        permissions = list(list(kind = "drive#permission", id = "15439814383658842389", 
            type = "user", emailAddress = "iragooding@gmail.com", 
            role = "writer", displayName = "Ira Gooding", photoLink = "https://lh3.googleusercontent.com/-34orrtbX8SA/AAAAAAAAAAI/AAAAAAAABs0/v-zqTiDWi38/s64/photo.jpg", 
            deleted = FALSE), list(kind = "drive#permission", 
            id = "04621402895158649126", type = "user", emailAddress = "jtleek@gmail.com", 
            role = "writer", displayName = "Jeff Leek", photoLink = "https://lh4.googleusercontent.com/-7GpEIoWyW9E/AAAAAAAAAAI/AAAAAAAAAws/tnc0V4vZK2k/s64/photo.jpg", 
            deleted = FALSE), list(kind = "drive#permission", 
            id = "anyoneWithLink", type = "anyone", role = "reader", 
            allowFileDiscovery = FALSE), list(kind = "drive#permission", 
            id = "15237212639967747286", type = "user", emailAddress = "muschellij2@gmail.com", 
            role = "owner", displayName = "John Muschelli", photoLink = "https://lh3.googleusercontent.com/-XP36b9P_2u4/AAAAAAAAAAI/AAAAAAAAAFU/duLcXDs5KAE/s64/photo.jpg", 
            deleted = FALSE)), permissionIds = list("15439814383658842389", 
            "04621402895158649126", "anyoneWithLink", "15237212639967747286"), 
        quotaBytesUsed = "0", isAppAuthorized = FALSE, exportLinks = list(
            `application/vnd.oasis.opendocument.presentation` = "https://docs.google.com/feeds/download/presentations/Export?id=1Opt6lv7rRi7Kzb9bI0u3SWX1pSz1k7botaphTuFYgNs&exportFormat=odp", 
            `application/pdf` = "https://docs.google.com/feeds/download/presentations/Export?id=1Opt6lv7rRi7Kzb9bI0u3SWX1pSz1k7botaphTuFYgNs&exportFormat=pdf", 
            `application/vnd.openxmlformats-officedocument.presentationml.presentation` = "https://docs.google.com/feeds/download/presentations/Export?id=1Opt6lv7rRi7Kzb9bI0u3SWX1pSz1k7botaphTuFYgNs&exportFormat=pptx", 
            `text/plain` = "https://docs.google.com/feeds/download/presentations/Export?id=1Opt6lv7rRi7Kzb9bI0u3SWX1pSz1k7botaphTuFYgNs&exportFormat=txt")))), row.names = 1L, class = c("dribble", 
"tbl_df", "tbl", "data.frame"))
res
```

Here we see the name, additional info, and the Google Slide deck ID.  We will use the first ID to grab information about that deck.

### Reading from a Google Slide deck (Google Slide Auth)

As you are authorized for Google Drive with MOOC-generator, let's get the info from the slides, including the exported PNG URL:

```{r slide_df}
slides = gs_slide_df(res$id[1])
slides
head(slides$png_url, 2)
```

We can also grab any notes from the deck if they exist:

```{r slide_notes}
notes = notes_from_slide(res$id[1])
head(notes, 3)
```

### Uploading a Video (YouTube Auth)

We do not authorize the Google Cloud Text-to-Speech APIs; that must be done outside `didactr`.  The [`ari` package](https://cran.r-project.org/package=ari) allows you to combine these slides and notes into a video (the default is to Amazon Polly).  If you'd like to use Google Language's API, you need to look at the documentation for the [`googleLanguageR` package](https://cran.r-project.org/package=googleLanguageR) and set `service = "google"`.  The `gs_ari` function wraps the downloading of slides to a PDF, converts the slides to a set of PNGs, extracts the notes, synthesizes the notes into spoken audio, and then weaves them into a video.

```{r gs_ari, eval = FALSE}
video = gs_ari(res$id[1], output = "example_video.mp4")
```

Once the video is created, it can be uploaded using the [`tuber` package](https://cran.r-project.org/package=tuber) package, which `didactr` calls in its functionality.

```{r upload, eval = FALSE}
uploaded = tuber::upload_video(file = "example_video.mp4", status = list(privacyStatus = "unlisted"))
```

The example output can be seen on https://www.youtube.com/watch?v=NJ5wGE2HtLk.  The YouTube `force-ssl` scope is the default authorization done for YouTube, but `tuber::yt_oauth` has other options.  When creating courses with MOOC-generator, you may want to get metrics from videos or delete videos, which can be done by `tuber`, which requires more than just read only access.  


